Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2017-11-27 draft1.2.tex
modified:   draft1.2.tex

\begin{figure}[tb]
 \begin{center}
(a) \includegraphics[height=0.46\textwidth,angle=-90]{images/N8p_E.eps}
(b) \includegraphics[height=0.46\textwidth,angle=-90]{images/N16p_E.eps}
 \end{center}
 \caption{Energy surface as functions of $j$
 for $x=0.5$, $x=2$ and $x=3.2$.
 Dashed line is the pairing deformation parameter $\alpha$
 of Eq.~(\ref{Delta_BCS}) as a function of $j$.
 (a) mid-shell ($\Omega=N=8$) and (b) closed-shell ($2\Omega=N=16$).
}
 \label{fig:p_Delta}
\end{figure}

@@

The collective model treatment
requires the collective wave functions to be well localized
in the $j<0$ region.
The potential energy, $E=\mathcal{H}(\phi=0,j;J)$, is also shown in
Fig.~\ref{fig:p_Delta}.
The restriction becomes more serious for the stronger pairing cases.
For instance, the potential with $x=3.2$ in Fig.~\ref{fig:p_Delta}(a)
has only about 1 MeV depth at the minimum point, relative to the value
at the boundary point ($j=0$) with the maximum value of $\alpha$ ($\Delta$).

%If the system has a deep potential at $j<0$ to prevent the wave function
%from spreading toward the region of $j<0$,
%we may justify the use of $\alpha$ as a coordinate in
%the collective model.
%The importance of the region of $j<0$ is considerable in strong pairing case.
Figure~\ref{fig:Delta_E} shows two examples of the relationship 
between excitation energies and energy surface.
In the panel (a), we show the case of large $\Omega$
($\Omega=50$, $N=50$, $x=2.4$),
in which
the excited $0^+$ states are bound up to second excitation.
For very large degeneracy, the pocket of energy surface is deep, 
hence the low-lying excited states may be described by $\alpha$. 
However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, $x=2.4$)
of the panel (b), no excited states are bound.
This shallow pocket of potential energy is a consequence of the
choice of the collective coordinate
which represents only the $j<0$ region.
Therefore, the collective model treatment assuming
$\alpha$ ($\Delta$) as the collective coordinate
is not applicable to small-$\Omega$ and strong-pairing cases.

>>>>

\begin{figure}[tb]
 \begin{center}
(a) \includegraphics[height=0.46\textwidth,angle=-90]{images/N8p_E.eps}
(b) \includegraphics[height=0.46\textwidth,angle=-90]{images/N16p_E.eps}
 \end{center}
 \caption{Energy surface as functions of $j$,
 Eq. (\ref{TDHFB_Hamiltonian_3}) with $\phi=0$,
 for $x=0.5$, $x=2$ and $x=3.2$.
 Dashed line is the pairing deformation parameter $\alpha$
 of Eq.~(\ref{Delta_BCS}) as a function of $j$.
 (a) mid-shell ($\Omega=N=8$) and (b) closed-shell ($2\Omega=N=16$).
}
 \label{fig:p_Delta}
\end{figure}

@@

The collective model treatment
requires the collective wave functions to be well localized
in the $j<0$ region.
The potential energy, $E(j)=\mathcal{H}(\phi=0,j;J=N/2)$ of
Eq. (\ref{TDHFB_Hamiltonian_3}), is also shown in
Fig.~\ref{fig:p_Delta}.
The restriction becomes more serious for the stronger pairing cases.
For instance, the potential with $x=3.2$ in Fig.~\ref{fig:p_Delta}(a)
has only about 1 MeV depth at the minimum point, relative to the value
at the boundary point ($j=0$) corresponding to
the maximum value of $\alpha$ ($\Delta$).

%If the system has a deep potential at $j<0$ to prevent the wave function
%from spreading toward the region of $j<0$,
%we may justify the use of $\alpha$ as a coordinate in
%the collective model.
%The importance of the region of $j<0$ is considerable in strong pairing case.
To simulate the result of the collective model, we expand the Hamiltonian
(\ref{TDHFB_Hamiltonian_3}) up to the second order in $\phi$,
then, quantize it by $\hat{\phi}=i\partial/\partial j$ with
the ordering given by the Pauli's prescription.
The range of the coordinate $j$ is restricted to $j_{\rm min}\leq j \leq 0$
with the vanishing boundary condition $\psi(j_{\rm min})=\psi(0)=0$.
Figure~\ref{fig:Delta_E} shows two examples of the relationship 
between excitation energies and the potential energy surface.
In the panel (a), we show the case of large $\Omega$
($\Omega=50$, $N=50$, $x=2.4$),
in which
the excited $0^+$ states are bound up to second excitation.
For very large degeneracy, the pocket of energy surface is deep, 
hence the low-lying excited states may be described by $\alpha$. 
However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, $x=2.4$)
of the panel (b), no excited states are bound.
This shallow pocket of potential energy is a consequence of the
choice of the collective coordinate
which represents only the $j<0$ region.
Therefore, the collective model treatment assuming
$\alpha$ ($\Delta$) as the collective coordinate
is not applicable to small-$\Omega$ and strong-pairing cases.
